---
title: "1. Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{1. Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)
```

## 1. Why `restbatch`

Many algorithms require minutes, hours, or even days to run. `restbatch` provides an implementation that runs in the background managing the running algorithms (tasks) and automatically dispatch to the clusters (if configured). The dispatcher (server) can be set as a service that runs even after the current session closed. For example:

Use-case 1: users can schedule tasks, let the tasks running without blocking the systems. They may even exit the session, and pick the results up next morning in another session. 

Use-case 2: R-shiny apps can schedule hundreds of tasks without freezing the front-end website. The tasks run even after current shiny sessions becoming expired. The users can retrieve their results in new sessions.

## 2. A simple show-case

### 2.1 Start a server

A local server can be started with a single line. This will start a service that runs in the background.

```{r setup}
restbatch::start_server()
#> Starting a restbatch server at http://127.0.0.1:7033
#> You have chosen this server to be the default server.
```

By default, the local server runs at port `7033` on the 'localhost' IP `127.0.0.1`. It only receives request from your own computer, and rejects requests from anyone else. The port `7033` will be occupied by the `restbatch` service. 

Once the service is started, it may take a while to get everything set up. you can use `server_alive` function to validate the server status.

```{r validate}
restbatch::server_alive()
#> [1] TRUE
#> attr(,"response")
#> Response [http://127.0.0.1:7033/validate/ping]
#>   Date: 2021-02-11 18:16
#>   Status: 200
#>   Content-Type: application/json
#>   Size: 652 B
#> 
```


Alternatively, you can use `ensure_server` to start a server, and wait until the server is ready.

```{r}
restbatch::ensure_server()
```


### 2.2 Create, submit, monitor, collect, restore, and remove a task

Let's approximate `pi` using the following function and we want to see how close approximation can be by setting different `n`.

```{r}
piApprox = function(n) {
  d = sqrt(runif(n)^2 + runif(n)^2)
  4 * mean(d <= 1)
}
```

1. Create a task: A task can be created via `new_task2`

```{r}
task <- restbatch::new_task2(function(x){
  set.seed(1000)
  piApprox(10^x)
}, x = 1:8, task_name = "demo_task")

task
#> Task (client proxy from the `restbatch` package)
#> Task name : [22dbdc9ec25174a768c15e03c7356780__demo_task__452ce031c6ba672d]
#> Total jobs: 8
#> Submitted to: [NA]
#> 
#> * Use `task$submit()` to submit this task
```

2. Submit a task: To start the task, submit to the `restbatch` server:

```{r}
task$submit()
```

3. Monitor a task: You can monitor and track the progress using `task$monitor()`. 

```
Task ID name: 22dbdc9ec25174a768c15e03c7356780__demo_task__452ce031c6ba672d
Task local path: /Users/dipterix/tasks/...

Task has not been submitted/scheduled. Please run the following command to 
submit task:

	task$submit()

Jobs submitted to: 127.0.0.1:7033

You can download the task results once it's finished: 
	http://127.0.0.1:7033/info/results?task_name=22dbdc9ec25174a768c15e03c7356780_
_demo_task__452ce031c6ba672d

Start listening to the server report...
6 finished out of 8
7 finished out of 8
8 finished out of 8

Task finished
```

Alternatively, you can use `task$resolved()`, or `task$server_status()` to check if it's finished.

```
task$resolved()
#> [1] TRUE

as.data.frame(task$server_status())
#>   status error           timestamp message n_total n_started n_done n_error
#> 1 finish FALSE 2021-02-11 14:40:23      OK       8         8      8       0
```

4. Restore a task: Once resolved, `collect` method will read the results into memory:

```{r}
unlist(task$collect())
#> [1] 3.200000 3.160000 3.196000 3.136000 3.146120 3.141448 3.141256 3.141440
```

5. Restore a task from another places: Once a task is created, you can always restore the results in another R session using `restore_task2` function. The task name can be obtained from previous `task$task_name` field.

```{r}
task_restored <- restbatch::restore_task2(
  task_name = "22dbdc9ec25174a768c15e03c7356780__demo_task__452ce031c6ba672d"
)

task_restored
#> Task (client proxy from the `restbatch` package)
#> Task name : [22dbdc9ec25174a768c15e03c7356780__demo_task__452ce031c6ba672d]
#> Total jobs: 8
#> Submitted to: http://127.0.0.1:7033/
#> Status for 8 jobs at 2021-02-11 14:48:42:
#>   Submitted    : 8 (100.0%)
#>   -- Queued    : 0 (  0.0%)
#>   -- Started   : 8 (100.0%)
#>   ---- Running : 0 (  0.0%)
#>   ---- Done    : 8 (100.0%)
#>   ---- Error   : 0 (  0.0%)
#>   ---- Expired : 0 (  0.0%)
#> 
#> *The task is finished, but the result has not been collected yet.
#> Use `task$collect()` to collect the results.
```

6. Remove a task: When a task is finished and will not be used anymore, it is always recommended to remove it. 

```{r}
task$remove()
#> [1] TRUE
```

Removing a task will erase the entire folders from both client and server side. 




